Tail Indices and Scale Parameters in Financial Time Series

### 2017-03-23 papers/FX/draft.tex
Checked the Hoga test again. Use my own implementation.

Figure \ref{fig:Energy_lower},
\ref{fig:Consumer_Staples_lower},
and \ref{fig:Information_Technology_lower}
show the Hill estimates of the
lower tail indices of the ``energy'', ``consumer staples'' and ``information
technology'' sectors of the S\&P 500 index, respectively.
\begin{figure}[htb!]
  \centering
  \begin{subfigure}[b]{\linewidth}
    \includegraphics[width=\textwidth, trim={0, 0.8cm, 0, 2cm}, clip]
                    {Energy_lower.pdf}
    \caption{``Energy'' sector of S\&P 500}
    \label{fig:Energy_lower}
  \end{subfigure}
  \begin{subfigure}[b]{\linewidth}
    \includegraphics[width=\textwidth, trim={0, 0.8cm, 0, 2cm}, clip]
                    {Consumer_Staples_lower.pdf}
    \caption{``Consumer Staples'' sector of S\&P 500}
    \label{fig:Consumer_Staples_lower}
  \end{subfigure}
  \begin{subfigure}[b]{\linewidth}
    \includegraphics[width=\textwidth, trim={0, 0.8cm, 0, 2cm}, clip]
                    {Information_Technology_lower.pdf}
    \caption{``Information Technology'' sector of S\&P 500}
    \label{fig:Information_Technology_lower}
  \end{subfigure}
  \caption{\small Hill estimates of lower tail indices of
    daily return series in sectors of Standard \& Poor
    500 index. Each circle coresponds to a Hill estimate; the grey
    triangles above and below it mark the 97.5\% and 2.5\% quantiles
    of its approximate normal distribution.
    The low and high red lines mark the median of the 2.5\% quantiles
    and median of the 97.5\% quantiles, respectively.
    The data are from {\it Yahoo Finance} and the labels on
    the horizontal axis are Yahoo symbols of the stocks. The data span
    from 2010-01-01 to 2015-01-01 and comprise $n=1304$
    observations. $k=50$ lower order statistics are used
    for computing $\alpha_n$. 
  }
\end{figure}

>>>>

Figure \ref{fig:Energy_lower},
\ref{fig:Consumer_Staples_lower},
and \ref{fig:Information_Technology_lower}
show the Hill estimates of the
lower tail indices of the ``energy'', ``consumer staples'' and ``information
technology'' sectors of the S\&P 500 index, respectively.
\begin{figure}[htb!]
  \centering
  \begin{subfigure}[b]{\linewidth}
    \includegraphics[width=\textwidth, trim={0, 0.8cm, 0, 2cm}, clip]
                    {Energy_lower.pdf}
    \caption{``Energy'' sector of S\&P 500}
    \label{fig:Energy_lower}
  \end{subfigure}
  \begin{subfigure}[b]{\linewidth}
    \includegraphics[width=\textwidth, trim={0, 0.8cm, 0, 2cm}, clip]
                    {Consumer_Staples_lower.pdf}
    \caption{``Consumer Staples'' sector of S\&P 500}
    \label{fig:Consumer_Staples_lower}
  \end{subfigure}
  \begin{subfigure}[b]{\linewidth}
    \includegraphics[width=\textwidth, trim={0, 0.8cm, 0, 2cm}, clip]
                    {Information_Technology_lower.pdf}
    \caption{``Information Technology'' sector of S\&P 500}
    \label{fig:Information_Technology_lower}
  \end{subfigure}
  \caption{\small Hill estimates of lower tail indices of
    daily return series in sectors of Standard \& Poor
    500 index. Each circle coresponds to a Hill estimate; the grey
    triangles above and below it mark the 97.5\% and 2.5\% quantiles
    of its approximate normal distribution.
    The low and high red lines mark the median of the 2.5\% quantiles
    and median of the 97.5\% quantiles, respectively.
    The data are from {\it Yahoo Finance} and the labels on
    the horizontal axis are Yahoo symbols of the stocks. The data span
    from 2010-01-01 to 2015-01-01 and comprise $n=1304$
    observations. $k=50$ lower order statistics are used
    for computing $\alpha_n$. 
  }
\end{figure}
One can see that all the confidence intervals of the ``Energy'' and
``Consumer Staples'' sectors overlap. Hence it is informative to test
the hypothesis that the tail indices of these return series are equal.
Hoga \cite{Hoga2017} devised tests for this purpose. We adopt his
approach but use our own implementation. The next section has more
details on this.

\subsection{Hoga's Test}
Hoga \cite{Hoga2017} devised tests for the change of a specified
extreme quantile.

We first test whether there is a change of tail indices in each of two
series, and if there is no change in either series, we concatenate
them and test for a change. Figure \ref{fig:Hoga_Energy_Single} shows
the test statistics of stocks in the ``Energy'' sector of the S\&P 500
index. Clearly, the null hypothesis, i.e. there is a change in the
extreme quantile can not be rejected at the specified significance
level for any of the stocks.
\begin{figure}[htb!]
  \centering
  \includegraphics[width=\textwidth]{Hoga_Energy_Single.pdf}
  \caption{Hoga Test Statistics}
  \label{fig:Hoga_Energy_Single}
\end{figure}

% Figure \ref{fig:Hoga_Energy_pair} shows
% the test statistics of pairs of stocks in the ``Energy'' sector of the
% S\&P 500 index: We first order the stocks by their names and then
% concatenate the 1st to the 2nd to form the 1st sequence, the 2nd and
% the 3rd to form the 2nd sequence, and so forth.

% Clearly, the null hypothesis, i.e. there is a change in the
% extreme quantile  can not be rejected at the specified significance
% level for any of the stocks.
